Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-03-02 paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The main difference between embedded systems and CPSs is indeed the strong presence of modern communication technologies ({\it e.g.}, Internet of Things - IoT) in the latter. This simple difference causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging CPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a CPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services; however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if read and write operations are performed according to what is specified in the device's datasheet and setup periods are respected. In summary, the main goal would be to ensure that the developed driver is compliant with the underlying hardware, which goes further than code correctness and also tackles the interaction with surrounding entities.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency) must be considered during verification~\cite{Kroening15}. Such observations expand the addressed issues and even complement what was mentioned in the last paragraphs.

>>>>

The main difference between embedded systems and CPSs is indeed the strong presence of modern communication technologies ({\it e.g.}, Internet of Things - IoT) in the latter. This simple difference causes a revolution in terms of flexibility, scalability, and complexity of those systems and adds a novel class of problems to the challenges found in the embedded systems domain. For example, micro-grids, {\it i.e.}, small-scale electricity systems that gather different sources of distributed generation (DG) and loads, are emerging CPSs, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. One may also notice that each DG element and the majority of current loads already employ embedded software and present several safety-critical requirements; however, the integration of both constitute a CPS, where additional challenges related to synchronization, stability, control, communication, and reliability of the entire micro-grid arise.

@@

For instance, one may argue that a Linux device driver \cite{ldd} was verified and correctly uses the related kernel services; however, not much can be said about correct access to the associated hardware and its use, {\it i.e.}, if \textit{read} and \textit{write} operations are performed according to what is specified in the device's datasheet and setup periods are respected. In summary, the main goal would be to ensure that the developed driver is compliant with the underlying hardware, which goes further than code correctness and also tackles the interaction with surrounding entities.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software domain, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, interfacing, and concurrency) must be considered during verification~\cite{Kroening15}. Such observations expand the addressed issues and even complement what was mentioned in the previous paragraphs.
